---
title: "Project1_zg2245 part1"
output:
  html_document: default
  html_notebook: default
---

As an art of spoken language, public speeches came into being with the existence of man, and have developed with the development of society. Over two hundred years, from George Washington to Donald Trump, the presidents expressed their best wishes and heroic dreams, displayed their rare gifts, bold strategies as well as administrative programmes through inaugural speeches. By carefully analyse and research, the author substantiates the propositions as follows. One of the most important aspects of language is that it is never stagnant. It is constantly changing to accommodate the society it serves. For these speeches which span over two centuries, their language style change with time flying and social development.

# Step 0: check and install needed packages. Load the libraries and functions. 

```{r, message=FALSE, warning=FALSE}
packages.used=c("rvest", "wordcloud","tibble", "qdap", 
                "sentimentr", "gplots", "dplyr",
                "tm", "syuzhet", "factoextra", 
                "beeswarm", "scales", "RColorBrewer",
                "RANN", "tm", "topicmodels", "tidytext")

# check packages that need to be installed.
packages.needed=setdiff(packages.used, 
                        intersect(installed.packages()[,1], 
                                  packages.used))
# install additional packages
if(length(packages.needed)>0){
  install.packages(packages.needed, dependencies = TRUE)
}

# load packages
library("rvest")
library("tibble")
library("qdap")
library("sentimentr")
library("gplots")
library("dplyr")
library("tm")
library("syuzhet")
library("factoextra")
library("beeswarm")
library("scales")
library("RColorBrewer")
library("RANN")
library("tm")
library("topicmodels")
library("wordcloud")
library("tidytext")
source("../lib/plotstacked.R")
source("../lib/speechFuncs.R")
```

# Step 1: Data preparing. In this part, we scrape data from the internet and transform it into an ideal form.
```{r, message=FALSE, warning=FALSE}
### Inauguaral speeches
main.page <- read_html(x = "http://www.presidency.ucsb.edu/inaugurals.php")
# Get link URLs
# f.speechlinks is a function for extracting links from the list of speeches. 
inaug=f.speechlinks(main.page)
#head(inaug)
as.Date(inaug[,1], format="%B %e, %Y")
inaug=inaug[-nrow(inaug),] # remove the last line, irrelevant due to error.

#### Nomination speeches
main.page=read_html("http://www.presidency.ucsb.edu/nomination.php")
# Get link URLs
nomin <- f.speechlinks(main.page)
#head(nomin)
#
#### Farewell speeches
main.page=read_html("http://www.presidency.ucsb.edu/farewell_addresses.php")
# Get link URLs
farewell <- f.speechlinks(main.page)
#head(farewell)
inaug.list=read.csv("../data/inauglist.csv", stringsAsFactors = FALSE)
nomin.list=read.csv("../data/nominlist.csv", stringsAsFactors = FALSE)
farewell.list=read.csv("../data/farewelllist.csv", stringsAsFactors = FALSE)
speech.list=rbind(inaug.list, nomin.list, farewell.list)
speech.list$type=c(rep("inaug", nrow(inaug.list)),
                   rep("nomin", nrow(nomin.list)),
                   rep("farewell", nrow(farewell.list)))
speech.url=rbind(inaug, nomin, farewell)
speech.list=cbind(speech.list, speech.url)
# Loop over each row in speech.list
speech.list$fulltext=NA
for(i in seq(nrow(speech.list))) {
  text <- read_html(speech.list$urls[i]) %>% # load the page
    html_nodes(".displaytext") %>% # isloate the text
    html_text() # get the text
  speech.list$fulltext[i]=text
  # Create the file name
  filename <- paste0("../data/fulltext/", 
                     speech.list$type[i],
                     speech.list$File[i], "-", 
                     speech.list$Term[i], ".txt")
  sink(file = filename) %>% # open file to write 
  cat(text)  # write the file
  sink() # close the file
}
speech1=paste(readLines("../data/fulltext/SpeechDonaldTrump-NA.txt", 
                  n=-1, skipNul=TRUE),
              collapse=" ")
speech2=paste(readLines("../data/fulltext/SpeechDonaldTrump-NA2.txt", 
                  n=-1, skipNul=TRUE),
              collapse=" ")
speech3=paste(readLines("../data/fulltext/PressDonaldTrump-NA.txt", 
                  n=-1, skipNul=TRUE),
              collapse=" ")

Trump.speeches=data.frame(
  President=rep("Donald J. Trump", 3),
  File=rep("DonaldJTrump", 3),
  Term=rep(0, 3),
  Party=rep("Republican", 3),
  Date=c("August 31, 2016", "September 7, 2016", "January 11, 2017"),
  Words=c(word_count(speech1), word_count(speech2), word_count(speech3)),
  Win=rep("yes", 3),
  type=rep("speeches", 3),
  links=rep(NA, 3),
  urls=rep(NA, 3),
  fulltext=c(speech1, speech2, speech3)
)

speech.list=rbind(speech.list, Trump.speeches)
sentence.list=NULL
for(i in 1:nrow(speech.list)){
  sentences=sent_detect(speech.list$fulltext[i],
                        endmarks = c("?", ".", "!", "|",";"))
  if(length(sentences)>0){
    emotions=get_nrc_sentiment(sentences)
    word.count=word_count(sentences)
    # colnames(emotions)=paste0("emo.", colnames(emotions))
    # in case the word counts are zeros?
    emotions=diag(1/(word.count+0.01))%*%as.matrix(emotions)
    sentence.list=rbind(sentence.list, 
                        cbind(speech.list[i,-ncol(speech.list)],
                              sentences=as.character(sentences), 
                              word.count,
                              emotions,
                              sent.id=1:length(sentences)
                              )
    )
  }
}
sentence.list=
  sentence.list%>%
  filter(!is.na(word.count)) 
sel.comparison=c("DonaldJTrump","JohnMcCain", "GeorgeBush", "MittRomney", "GeorgeWBush",
                 "RonaldReagan","AlbertGore,Jr", "HillaryClinton","JohnFKerry", 
                 "WilliamJClinton","HarrySTruman", "BarackObama", "LyndonBJohnson",
                 "GeraldRFord", "JimmyCarter", "DwightDEisenhower", "FranklinDRoosevelt",
                 "HerbertHoover","JohnFKennedy","RichardNixon","WoodrowWilson", 
                 "AbrahamLincoln", "TheodoreRoosevelt", "JamesGarfield", 
                 "JohnQuincyAdams", "UlyssesSGrant", "ThomasJefferson",
                 "GeorgeWashington", "WilliamHowardTaft", "AndrewJackson",
                 "WilliamHenryHarrison", "JohnAdams")
```
# Step 2: Sentence length

The seriousness of the speaker's attitude can be revealed through examining sentence length. Sentence length is usually regarded as one of the linguistic markers measuring the degree of formality: the greater the sentence length, the more formal the language. The below table shows that, although the sentence length of the speeches decreased constantly, it still much longer than that of daily conversations which is about 12 words on average and than that of all English sentences on the whole which is 17.6 words per sentence. On the other hand, the variation of sentence length of those speeches results from that in the course of more than 200 years, the way people manage language changes.

```{r, fig.width = 3, fig.height = 3}
sentence.list.sel=sentence.list%>%filter(type=="inaug", File%in%sel.comparison, Term==1)
sentence.list.sel$File=factor(sentence.list.sel$File)

sentence.list.sel$FileOrdered=reorder(sentence.list.sel$File, 
                                  sentence.list.sel$word.count, 
                                  mean, 
                                  order=T)
par(mar=c(4, 11, 2, 2))

beeswarm(word.count~FileOrdered, 
         data=sentence.list.sel,
         horizontal = TRUE,
         pch=16, col=alpha(brewer.pal(9, "Set1"), 0.6), 
         cex=0.55, cex.axis=0.8, cex.lab=0.8,
         spacing=5/nlevels(sentence.list.sel$FileOrdered),
         las=2, ylab="", xlab="Number of words in a sentence.",
         main="Inaugural Speeches")
```

# Step 3: Sentiment analsis

Take William J. Clinton, Donald Trump, Barack Obama, George W. Bush as examples, Trump and Bush's speeches are more colorful than the other two's. This is not olny because of the personality but also because of the certain circumstance.

```{r, fig.height=2.5, fig.width=2}
par(mfrow=c(4,1), mar=c(1,0,2,0), bty="n", xaxt="n", yaxt="n", font.main=1)

f.plotsent.len(In.list=sentence.list, InFile="WilliamJClinton", 
               InType="nomin", InTerm=1, President="William J. Clinton")

f.plotsent.len(In.list=sentence.list, InFile="DonaldJTrump", 
               InType="nomin", InTerm=1, President="Donald Trump")

f.plotsent.len(In.list=sentence.list, InFile="BarackObama", 
               InType="nomin", InTerm=1, President="Barack Obama")

f.plotsent.len(In.list=sentence.list, InFile="GeorgeWBush", 
               InType="nomin", InTerm=1, President="George W. Bush")
```

By cluster analysis, we can divide all speeches into 5 groups for different emotion patterns. Here chronology is not the main aspect. Personality and circumstance matter.

```{r, fig.height=3.3, fig.width=3.7}
presid.summary=tbl_df(sentence.list)%>%
  filter(type=="nomin", File%in%sel.comparison)%>%
  #group_by(paste0(type, File))%>%
  group_by(File)%>%
  summarise(
    anger=mean(anger),
    anticipation=mean(anticipation),
    disgust=mean(disgust),
    fear=mean(fear),
    joy=mean(joy),
    sadness=mean(sadness),
    surprise=mean(surprise),
    trust=mean(trust)
    #negative=mean(negative),
    #positive=mean(positive)
  )

presid.summary=as.data.frame(presid.summary)
rownames(presid.summary)=as.character((presid.summary[,1]))
km.res=kmeans(presid.summary[,-1], iter.max=200,
              5)
fviz_cluster(km.res, 
             stand=F, repel= TRUE,
             data = presid.summary[,-1], xlab="", xaxt="n",
             show.clust.cent=FALSE)
```

